### 2017-04-08 chapters/03-methodology.tex
Add stress tests results
re-structure paper

% TODO: add something about:
%       - hardware choices
%       - software choices
%       - language choices
%
%       - overall arch (flight platform, ground segmetn)

@@

\section{Radio Communications}

@@

This solution was tested using a Raspberry Pi 3 for the \acrlong{obc}, and an
Arduino UNO board for the payload. An unforeseen electrical engineering issue
required slight redesign of the system: on both the Arduino or the Raspberry
Pi, a small voltage, even inferior to the logic high (\SI{3.3}{V} on Raspberry
Pi, \SI{5}{V} on the Arduino UNO) was enough for the line to be read as a
logical high. This caused certain bursts of noise in the lines to be detected
by the \acrshort{obc} as a high CR line, even though the payload had not
raised it. This was fixed by using inverted logic: a payload would signal 
available data by pulling the \(\overline{CE}\) line low, and the \acrshort{obc}
would pull \(\overline{CR}\) low when addressing a payload.

@@

\subsection{Arduino Implementation}

\section{Flight Software}
\label{sec:flight-software}

\subsection{Architecture}

\subsection{User Interface}

>>>>

\section{Proposed Solution}

@@

\section{Environment}

\section{Development Approach}

\section{Radio Communications}
\label{sec:radio-coms}

@@

This solution was tested using a Raspberry Pi 3 for the \acrlong{obc}, and an
Arduino UNO board for the payload. An unforeseen electrical engineering issue
required a slight redesign of the system: on both the Arduino or the Raspberry
Pi, a small voltage, even inferior to the logic high (\SI{3.3}{V} on Raspberry
Pi, \SI{5}{V} on the Arduino UNO) was enough for the line to be read as a
logical high. This caused certain bursts of noise in the lines to be detected
by the \acrshort{obc} as a high CR signal, even though the payload had not
raised it. This was fixed by using inverted logic: a payload would signal 
available data by pulling the \(\overline{CE}\) line low, and the \acrshort{obc}
would pull \(\overline{CR}\) low when addressing a payload.

@@

% TODO

\section{Flight Platform}
\label{sec:flight-software}

\subsection{Hardware Prototype}

\subsection{Flight Software}

\subsubsection{Payload Priority System}

\subsubsection{Mission Design and Configuration Files}

### 2017-04-08 chapters/04-results.tex
re-structure paper

Figure \ref{fig:stress-fec} shows that in all three tests, the amount of bytes
that were corrected using the frames' \acrlong{ecc} was similar. As expected,
the test with the highest byte error rate shows a slightly inferior correction
rate – frames that contain more than 16 erroneous bytes cannot be corrected at
all. Table \ref{tab:stress-fec} shows that the actual error correction rates
are close to the theoretical byte error rates induced at transmission as long
as the those theoretical rates are below the theoretical maximum.

@@

>>>>

Figure \ref{fig:stress-fec} shows that in all three tests, the amount of bytes
that were corrected using the frames' \acrlong{ecc} was similar. As expected,
the test with the highest byte error rate shows a slightly inferior correction
rate – frames that contain more than 16 erroneous bytes cannot be corrected at
all.

@@

Table \ref{tab:stress-fec} shows that the reported error correction rates
are slightly less than the theoretical error rates induced at transmission as
long as the these theoretical rates are below the maximum acceptable rate, and
fall well below when the error rate is above the limit.

\begin{table}[H]
\begin{center}
\begin{tabular}{ |c|c c| }
\hline
test & Correction Rate & Theoretical Error Rate \\
\hline
$\frac{8}{256}$  & \SI{2.826}{\percent} & \SI{3.125}{\percent} \\ [0.2em]
$\frac{14}{256}$ & \SI{3.655}{\percent} & \SI{5.469}{\percent} \\ [0.2em]
$\frac{18}{256}$ & \SI{2.514}{\percent} & \SI{7.031}{\percent} \\ [0.2em]
\hline 
\end{tabular}
\end{center}
\caption {DITL Test - Platform health data}
\label{tab:stress-fec}
\end{table}
